---
title: "Step 2: Plot Configurations"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
```

This manual provides an explanation of the file `2.PlotGens.R`

<div class="info-box">
  <strong>❗ Important:</strong>
  <ul style="margin-top: 8px; padding-left: 20px;">
    <li>You must run <code>1.ProjectSetup</code> with <code>plot_data &lt;- TRUE</code> before running this script.</li>
    <li>You can simply copy and paste any plot code from this manuscript and replace the original code in <code>2.PlotGens.R</code>.</li>
  </ul>
</div>

This manual provides an explanation of the file `2.PlotGens.R`

If you are unsure, please refer to: [Plot Catalogs](https://pattawee.shinyapps.io/gtapviz-advanced-plot-configs/)

You may define a custom output folder to create separate directories for each plot.
```{r, eval=FALSE}
# Define new output location (or leave it as deafult)
output.folder <- output.folder
```


# Input Data {.unnumbered}

Define the dataframe to be plotted using either `sl4.plot.data` or `har.plot.data`,  
obtained by running `1.ProjectSetup.R` with `plot_data = TRUE`.

Depending on your data extraction method, you must assign the `dataframe`  
to be plotted from the corresponding data list.

<details>
  <summary class="toggle-summary">🔍 Extracting Data Frames</summary>
  
  <div class="tip-box">

**All plot functions require a data frame as an input, so you must unlist the data structure before using it.**

This an example of how to extract the dataframe from the data list:
```{r, eval=FALSE}
comparison_plot_data <- sl4.plot.data[["REG"]]     
detail_plot_data <- sl4.plot.data[["COMM*REG"]]     
stack_plot_data <- har.plot.data[["A"]]
```

If you used the data extraction method `group_data_by_dims`, you may need to define the plot data as follows:
```{r, eval=FALSE}
plot_data <- sl4.plot.data[["Sector"]][["REG"]]
```

  </div>
</details>


# Plot Setup {.unnumbered}

Do not forget to change export parameters to TRUE!

- `export_picture_c = TRUE`

- `export_as_pdf_c = "merged" or TRUE` (merged will combine all plots into one PDF file)

---
<p style="color:#8B0000; font-size:2.5rem; text-align:center;">
  <strong>Time to copy and paste code to your R script!</strong>
</p>

# Comparison Plot
<details>
  <summary class="toggle-summary">💻 Comparison Plot Codes</summary>
```{=html}
<!-- START: Comparison Plot Filter UI -->
<style>
  label { font-weight: bold; }
  select { font-size: 16px; margin-bottom: 20px; padding: 5px 10px; width: 300px;}
  pre { background-color: #f4f4f4; padding: 15px; border-left: 5px solid #1C3E5D; overflow-x: auto; }
  .code-box { display: none; }
</style>

<label for="plotFilterComparison">Choose Codes:</label>
<select id="plotFilterComparison">
  <option value="comparison">Default</option>
  <option value="macro">GTAP Macro Plot</option>
  <option value="advanced">Advanced Comparison Plot</option>
</select>

<div class="code-group-comparison">

<div id="comparison" class="code-box">
<p>This function is suitable for one-dimensional data such as <code>qgdp</code>, <code>u</code>, <code>EV</code>, or <code>qpriv</code>, allowing comparison of effects across regions (e.g., <code>REG</code>).</p>

<pre><code>
# For help function use: ?comparison_plot
comparison.data <- sl4.plot.data[["REG"]]   # Replace with your actual dataframe name

default_compare.plot <- comparison_plot(  # ! Do not change this line
  data                      = comparison.data,
  x_axis_from               = "Region",         # Column used for the x-axis
  filter_var                = NULL,             # Optional column to filter data based on x-axis
  split_by                  = "Variable",       # Column(s) used to split data into separate plots
  panel_var                 = "Experiment",     # Column used for paneling (faceting)
  invert_axis               = FALSE,            # Whether to invert the panel (facet) order
  separate_figure           = FALSE,            # Whether to generate a separate figure for each panel
  var_name_by_description   = FALSE,            # Use description as variable name
  add_var_info              = FALSE,            # Add variable code in parentheses
  export_picture            = TRUE,             # Export as image
  export_as_pdf             = "merged",         # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,
  
  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly
  export_config = create_export_config(
    width  = 28,
    height = 15
  ),
  
  # Some Plot Style Configurations
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "dynamic",                         # dynamic allows use of {Description}
      text = "Impacts on {Description}",
      sep  = ""
    ),
    all_font_size = 1,
    panel_rows    = 1,
    panel_cols    = NULL,
    color_tone    = "gtap"
  )
)
</code></pre>
</div>

    
<div id="macro" class="code-box"> 
<p>This function is suitable for global impacts (i.e., no dimensions); it uses data from the <code>Macros</code> header in the <code>sl4</code> solution file.</p>

<pre><code>
# For help function use: ?comparison_plot
comparison.data <- GTAPMacro   # Replace with your actual dataframe name

default_compare.plot <- comparison_plot(  # ! Do not change this line
  data                      = comparison.data,
  x_axis_from               = "Variable",       # Column used for the x-axis
  filter_var                = NULL,             # Optional column to filter data based on x-axis
  split_by                  = "Variable",       # Column(s) used to split data into separate plots
  panel_var                 = "Experiment",     # Column used for paneling (faceting)
  invert_axis              = TRUE,             # Whether to invert the panel (facet) order
  separate_figure           = FALSE,            # Whether to generate a separate figure for each panel
  var_name_by_description   = FALSE,            # Use description as variable name
  add_var_info              = FALSE,            # Add variable code in parentheses
  export_picture            = TRUE,             # Export as image
  export_as_pdf             = "merged",         # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,

  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly  
  export_config = create_export_config(
    width  = 28,
    height = 35
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "full",                            # Full title with static text
      text = "Global Economic Impacts",
      sep  = ""
    ),
    all_font_size = 1,
    panel_rows    = 1,
    panel_cols    = NULL,
    color_tone    = "grey_mono"     # Add "_mono" to use a single color for all bars
  )
)
  </code></pre>
  </div>
    


<div id="advanced" class="code-box">
<p>This R script is designed for full customization—everything must be defined from scratch. Please refer to the <strong>Plot Style Configs</strong> section before using it.</p>

<pre><code>
# For help function use: ?comparison_plot
comparison.data <- your_dataframe  # Replace with your actual dataframe name

adv.compare.plot <- comparison_plot(
  data = comparison.data,
  x_axis_from             = "Region",
  filter_var              = NULL,
  split_by                = NULL,
  panel_var               = "Experiment",
  variable_col            = "Variable",
  unit_col                = "Unit",
  desc_col                = "Description",
  invert_axis            = FALSE,
  separate_figure         = FALSE,
  var_name_by_description = FALSE,
  add_var_info            = FALSE,
  export_picture          = FALSE,
  export_as_pdf           = FALSE,
  output_path             = "/your/path",
  
  # Output Configurations
  export_config           = create_export_config(
    width = NULL,
    height = NULL,
    dpi = 300,
    bg = "white",
    limitsize = FALSE
  )
  
  # All Plot Configurations
  plot_style_config = create_plot_style(
    
    # Title settings
    show_title = TRUE,
    title_face = "bold",
    title_size = 20,
    title_hjust = 0.5,
    add_unit_to_title = TRUE,
    title_margin = c(10, 0, 10, 0), #c(top, right, bottom, left)
    
    title_format = create_title_format(
      type = "standard", #option: standard (default), prefix, suffix, full, dynamic
      text = "",
      sep = ""
    ),
    
    # X-Axis settings
    show_x_axis_title = TRUE,
    x_axis_title_face = "bold",
    x_axis_title_size = 16,
    x_axis_title_margin = c(25, 25, 0, 0), #c(top, right, bottom, left)
    show_x_axis_labels = TRUE,
    x_axis_text_face = "plain",
    x_axis_text_size = 14,
    x_axis_text_angle = 0,
    x_axis_text_hjust = 0,
    x_axis_description = "",
    
    # Y-Axis settings
    show_y_axis_title = TRUE,
    y_axis_title_face = "bold",
    y_axis_title_size = 16,
    y_axis_title_margin = c(25, 25, 0, 0), #c(top, right, bottom, left)
    show_y_axis_labels = TRUE,
    y_axis_text_face = "plain",
    y_axis_text_size = 14,
    y_axis_text_angle = 0,
    y_axis_text_hjust = 0,
    y_axis_description = "",
    show_axis_titles_on_all_facets = TRUE,
    
    # Value Labels
    show_value_labels = TRUE,
    value_label_face = "plain",
    value_label_size = 5,
    value_label_position = "above",
    value_label_decimal_places = 2,
    
    # Legend
    show_legend = FALSE,
    show_legend_title = FALSE,
    legend_position = "bottom",
    legend_title_face = "bold",
    legend_text_face = "plain",
    legend_text_size = 14,
    
    # Panel Strip
    strip_face = "bold",
    strip_text_size = 16,
    strip_background = "lightgrey",
    strip_text_margin = c(10, 0, 10, 0), #c(top, right, bottom, left)
    
    # Panel Layout
    panel_spacing = 2,
    panel_rows = NULL,
    panel_cols = NULL,
    theme = NULL,
    
    # Colors and Grid 
    color_tone = NULL,
    color_palette_type = "qualitative", #option: qualitative, sequential, diverging
    positive_color = "#2E8B57",
    negative_color = "#CD5C5C",
    background_color = "white",
    grid_color = "grey90",
    show_grid_major_x = FALSE,
    show_grid_major_y = FALSE,
    show_grid_minor_x = FALSE,
    show_grid_minor_y = FALSE,
    
    # Zero Line
    show_zero_line = TRUE,
    zero_line_type = "dashed",
    zero_line_color = "black",
    zero_line_size = 0.5,
    zero_line_position = 0,
    
    # Bar Chart
    bar_width = 0.9,
    bar_spacing = 0.9,
    
    # Scale Settings
    scale_limit = NULL,
    scale_increment = NULL,
    
    # Scale Expansion
    expansion_y_mult = c(0.05, 0.1),
    expansion_x_mult = c(0.05, 0.05),
    
    # Font Size Control
    all_font_size = 1,
    
    # Data Sorting
    sort_data_by_value = FALSE,
    
    # Plot Margin
    plot.margin = c(10, 25, 10, 10) #c(top, right, bottom, left)
  )
)
</code></pre>
</div>


</div>

<script>
  const selectComparison = document.getElementById("plotFilterComparison");
  const boxesComparison = document.querySelectorAll(".code-group-comparison .code-box");

  function showComparison() {
    boxesComparison.forEach(box => box.style.display = "none");
    const selected = selectComparison.value;
    const box = document.getElementById(selected);
    if (box) box.style.display = "block";
  }

  selectComparison.addEventListener("change", showComparison);
  showComparison();
</script>
<!-- END -->
```
</details>

<br>

# Detail Plot
<details>
  <summary class="toggle-summary">💻 Detail Plot Codes</summary>
```{=html}
<!-- START: Detail Plot Filter UI -->
<style>
  label { font-weight: bold; }
  select { font-size: 16px; margin-bottom: 20px; padding: 5px 10px; width: 300px; }
  pre { background-color: #f4f4f4; padding: 15px; border-left: 5px solid #1C3E5D; overflow-x: auto; }
  .code-box { display: none; }
</style>

<label for="plotFilterDetail">Choose Codes:</label>
<select id="plotFilterDetail">
  <option value="default_detail">Default</option>
  <option value="oned_detail">One dimensional data</option>
  <option value="twod_detail">Two dimensional data</option>
  <option value="threed_detail">Three dimensional data</option>
  <option value="top_impact_detail">Top Impact Filter</option>
  <option value="advanced_detail">Advanced Detail Plot</option>
</select>

<div class="code-group-detail">

<div id="default_detail" class="code-box">
<p>This function is suitable for any dimensional data, with a focus on detailed overviews rather than comparisons across a few observations—such as plotting <code>qgdp</code> for all countries.</p>

<p><strong>Note:</strong> <code>"REG"</code> has been renamed to <code>"Region"</code>, and <code>"COMM"</code> to <code>"Commodity"</code>.</p>

<pre><code>
# For help function use: ?detail_plot
detail.data <- sl4.plot.data[["COMM*REG"]]  # Replace with your actual dataframe

default_detail <- detail_plot(
  data                      = detail.data,
  x_axis_from               = "Commodity",      # Column used for the x-axis
  filter_var                = NULL,             # Optional column to filter data based on x-axis
  split_by                  = "Region",         # Column(s) used to split data into separate plots (e.g., one plot per variable)
  panel_var                 = "Experiment",     # Column used for paneling (faceting)
  top_impact                = NULL,             # Optionally limit to top-N most impactful entries per panel (e.g., top_impact = 10)
  invert_axis              = TRUE,             # Whether to invert the panel (facet) order
  separate_figure           = FALSE,            # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,             # Use the description as the variable name (e.g., qgdp becomes Real GDP)
  add_var_info              = FALSE,            # Add variable code in parentheses (e.g., Real GDP (qgdp))
  export_picture            = FALSE,            # Export the plots as image files
  export_as_pdf             = FALSE,            # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,
  
    # Output Configurations
    ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly     
    export_config = create_export_config(  
    width  = 23,              # Width of the output plot in inches
    height = 9                # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "prefix",        # option: standard (default), prefix, suffix, full, dynamic
      text = "Change in",
      sep  = " - "
    ),
    positive_color = "#2E8B57",  # Color for positive values
    negative_color = "#CD5C5C",  # Color for negative values
    all_font_size  = 1.1,        # Scale for all font sizes in the plot 
    panel_rows     = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols     = NULL        # Number of columns for the panel layout, NULL for automatic calculation
  )
)
</code></pre>
  </div>

<div id="oned_detail" class="code-box">
  <p>This R script is designed for one-dimensional data plot like <code>qgdp</code>, <code>EV</code>, etc. across all regions</p>
  
  <pre><code>
# For help function use: ?detail_plot
detail.data <- sl4.plot.data[["REG"]]   # Dataframe with one-dimensional data

oned_detail <- detail_plot(
  data                      = detail.data,
  x_axis_from               = "Region",         # Column used for the x-axis
  filter_var                = NULL,             # Optional column to filter data based on x-axis
  split_by                  = "Variable",       # Column(s) used to split data into separate plots
  panel_var                 = "Experiment",     # Column used for paneling (faceting)
  top_impact                = NULL,             # Optionally limit to top-N most impactful entries per panel
  invert_axis              = TRUE,             # Whether to invert the panel (facet) order
  separate_figure           = FALSE,            # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,             # Use the description as the variable name (e.g., qgdp becomes Real GDP)
  add_var_info              = FALSE,            # Add variable code in parentheses (e.g., Real GDP (qgdp))
  export_picture            = TRUE,             # Export the plots as image files
  export_as_pdf             = "merged",         # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,

  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly     
  export_config = create_export_config(
    width  = 35,              # Width of the output plot in inches
    height = 25               # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "prefix",        # option: standard (default), prefix, suffix, full, dynamic
      text = "Change in",
      sep  = " - "
    ),
    positive_color = "#2E8B57",  # Color for positive values
    negative_color = "#CD5C5C",  # Color for negative values
    all_font_size  = 1.1,        # Scale for all font sizes in the plot 
    panel_rows     = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols     = NULL        # Number of columns for the panel layout, NULL for automatic calculation  
  )
)
</code></pre>
  </div>
  
<div id="twod_detail" class="code-box">
  <p>This R script is designed for two-dimensional data plot like <code>qo</code>, <code>qxw</code>, <code>qmw</code>, etc., impacts across all regions (<code>"REG"</code>).</p>  

<pre><code>
# For help function use: ?detail_plot
detail.data <- sl4.plot.data[["COMM*REG"]]   # Dataframe with two-dimensional data

twod_detail <- detail_plot(
  data                      = detail.data,
  x_axis_from               = "Commodity",     # Column used for the x-axis
  filter_var                = NULL,            # Optional column to filter data based on x-axis
  split_by                  = "Variable",      # Column(s) used to split data into separate plots
  panel_var                 = "Experiment",    # Column used for paneling (faceting)
  top_impact                = NULL,            # Optionally limit to top-N most impactful entries per panel
  invert_axis              = TRUE,            # Whether to invert the panel (facet) order
  separate_figure           = FALSE,           # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,            # Use the description as the variable name
  add_var_info              = FALSE,           # Add variable code in parentheses
  export_picture            = FALSE,           # Export the plots as image files
  export_as_pdf             = FALSE,           # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,

  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly    
  export_config = create_export_config(
    width  = 45,             # Width of the output plot in inches
    height = 15              # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "prefix",       # option: standard (default), prefix, suffix, full, dynamic
      text = "Change in",
      sep  = " - "
    ),
    positive_color = "#2E8B57",  # Color for positive values
    negative_color = "#CD5C5C",  # Color for negative values
    all_font_size  = 1.1,        # Scale for all font sizes in the plot 
    panel_rows     = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols     = NULL        # Number of columns for the panel layout, NULL for automatic calculation  
  )
)
</code></pre>
  </div>
  
<div id="threed_detail" class="code-box">
  <p>This R script is designed for three-dimensional data plot like <code>qxs</code>. This example assumes that you chose to extract <code>qxs</code> during <strong>1.ProjectSetup</strong></p>

<p><strong>Note:</strong> This code can be applied to any dimensional data by adding more columns to <code>split_by</code>.</p>

  <pre><code>
# For help function use: ?detail_plot
detail.data <- bilateral_data[["qxs"]]   # Dataframe with three-dimensional data

threed_detail <- detail_plot(
  data                      = detail.data,
  x_axis_from               = "Commodity",     # Column used for the x-axis
  filter_var                = NULL,            # Optional column to filter data based on x-axis
  split_by                  = c("Source", "Destination"),  # Split plots by Source & Destination
  panel_var                 = "Experiment",    # Column used for paneling (faceting)
  top_impact                = NULL,            # Optionally limit to top-N most impactful entries per panel
  invert_axis              = TRUE,            # Whether to invert the panel (facet) order
  separate_figure           = FALSE,           # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,            # Use the description as the variable name
  add_var_info              = FALSE,           # Add variable code in parentheses
  export_picture            = FALSE,           # Export the plots as image files
  export_as_pdf             = FALSE,           # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,

  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly        
  export_config = create_export_config(
    width  = 45,             # Width of the output plot in inches
    height = 15              # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "dynamic",      # Use {Source} and {Destination} from column values
      text = "Change in bilateral trade between {Source} and {Destination}",
      sep  = ""
    ),
    positive_color = "#2E8B57",  # Color for positive values
    negative_color = "#CD5C5C",  # Color for negative values
    all_font_size  = 1.1,        # Scale for all font sizes in the plot 
    panel_rows     = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols     = NULL        # Number of columns for the panel layout, NULL for automatic calculation  
  )
)
</code></pre>
</div>

<div id="top_impact_detail" class="code-box">

<p>This function is similar to the "Default" code, but adds <code>top_impact = 10</code> to automatically filter the top 10 most impacted sectors (e.g., <code>x_axis_from = "Commodity"</code>).</p>

<pre><code>
# For help function use: ?detail_plot
## You can change `top_impact` to any numeric value.
detail.data <- sl4.plot.data[["COMM*REG"]]  # Replace with your actual dataframe

default_detail <- detail_plot(
  data                      = detail.data,
  x_axis_from               = "Commodity",      # Column used for the x-axis
  filter_var                = NULL,             # Optional column to filter data based on x-axis
  split_by                  = "Region",         # Column(s) used to split data into separate plots (e.g., one plot per variable)
  panel_var                 = "Experiment",     # Column used for paneling (faceting)
  top_impact                = NULL,             # Optionally limit to top-N most impactful entries per panel (e.g., top_impact = 10)
  invert_axis              = TRUE,             # Whether to invert the panel (facet) order
  separate_figure           = FALSE,            # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,             # Use the description as the variable name (e.g., qgdp becomes Real GDP)
  add_var_info              = FALSE,            # Add variable code in parentheses (e.g., Real GDP (qgdp))
  export_picture            = FALSE,            # Export the plots as image files
  export_as_pdf             = FALSE,            # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,
  
    # Output Configurations
    ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly     
    export_config = create_export_config(  
    width  = 23,              # Width of the output plot in inches
    height = 9                # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "prefix",        # option: standard (default), prefix, suffix, full, dynamic
      text = "Change in",
      sep  = " - "
    ),
    positive_color = "#2E8B57",  # Color for positive values
    negative_color = "#CD5C5C",  # Color for negative values
    all_font_size  = 1.1,        # Scale for all font sizes in the plot 
    panel_rows     = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols     = NULL        # Number of columns for the panel layout, NULL for automatic calculation
  )
)
</code></pre>
</div>

<div id="advanced_detail" class="code-box">
<p>This R script is designed for full customization—everything must be defined from scratch. Please refer to the <strong>Plot Style Configs</strong> section before using it.</p>

<pre><code>
# For help function use: ?detail_plot
detail.data <- sl4.plot.data[["COMM*REG"]]   # Replace with your actual dataframe name

adv.detail.plot <- detail_plot(
  data                    = detail.data,
  x_axis_from             = "Colname",
  filter_var              = NULL,
  split_by                = c("Var1", "Var2", "Var3"),
  panel_var               = "Experiment",
  variable_col            = "Variable",
  unit_col                = "Unit",
  desc_col                = "Description",
  top_impact              = NULL,
  invert_axis            = FALSE,
  separate_figure         = FALSE,
  var_name_by_description = FALSE,
  add_var_info            = FALSE,
  export_picture          = FALSE,
  export_as_pdf           = FALSE,
  output_path             = "/your/path",

  # Output Configurations
  export_config           = create_export_config(
    width = NULL,
    height = NULL,
    dpi = 300,
    bg = "white",
    limitsize = FALSE
  )
  
  # All Plot Configurations
  plot_style_config = create_plot_style(
    
    # Title settings
    show_title = TRUE,
    title_face = "bold",
    title_size = 20,
    title_hjust = 0.5,
    add_unit_to_title = TRUE,
    title_margin = c(10, 0, 10, 0), #c(top, right, bottom, left)
    
    title_format = create_title_format(
      type = "standard", #option: standard (default), prefix, suffix, full, dynamic
      text = "",
      sep = ""
    ),
    
    # X-Axis settings
    show_x_axis_title = TRUE,
    x_axis_title_face = "bold",
    x_axis_title_size = 16,
    x_axis_title_margin = c(25, 25, 0, 0), #c(top, right, bottom, left)
    show_x_axis_labels = TRUE,
    x_axis_text_face = "plain",
    x_axis_text_size = 14,
    x_axis_text_angle = 0,
    x_axis_text_hjust = 0,
    x_axis_description = "",
    
    # Y-Axis settings
    show_y_axis_title = TRUE,
    y_axis_title_face = "bold",
    y_axis_title_size = 16,
    y_axis_title_margin = c(25, 25, 0, 0), #c(top, right, bottom, left)
    show_y_axis_labels = TRUE,
    y_axis_text_face = "plain",
    y_axis_text_size = 14,
    y_axis_text_angle = 0,
    y_axis_text_hjust = 0,
    y_axis_description = "",
    show_axis_titles_on_all_facets = TRUE,
    
    # Value Labels
    show_value_labels = TRUE,
    value_label_face = "plain",
    value_label_size = 5,
    value_label_position = "above",
    value_label_decimal_places = 2,
    
    # Legend
    show_legend = FALSE,
    show_legend_title = FALSE,
    legend_position = "bottom",
    legend_title_face = "bold",
    legend_text_face = "plain",
    legend_text_size = 14,
    
    # Panel Strip
    strip_face = "bold",
    strip_text_size = 16,
    strip_background = "lightgrey",
    strip_text_margin = c(10, 0, 10, 0), #c(top, right, bottom, left)
    
    # Panel Layout
    panel_spacing = 2,
    panel_rows = NULL,
    panel_cols = NULL,
    theme = NULL,
    
    # Colors and Grid 
    color_tone = NULL,
    color_palette_type = "qualitative", #option: qualitative, sequential, diverging
    positive_color = "#2E8B57",
    negative_color = "#CD5C5C",
    background_color = "white",
    grid_color = "grey90",
    show_grid_major_x = FALSE,
    show_grid_major_y = FALSE,
    show_grid_minor_x = FALSE,
    show_grid_minor_y = FALSE,
    
    # Zero Line
    show_zero_line = TRUE,
    zero_line_type = "dashed",
    zero_line_color = "black",
    zero_line_size = 0.5,
    zero_line_position = 0,
    
    # Bar Chart
    bar_width = 0.9,
    bar_spacing = 0.9,
    
    # Scale Settings
    scale_limit = NULL,
    scale_increment = NULL,
    
    # Scale Expansion
    expansion_y_mult = c(0.05, 0.1),
    expansion_x_mult = c(0.05, 0.05),
    
    # Font Size Control
    all_font_size = 1,
    
    # Data Sorting
    sort_data_by_value = FALSE,
    
    # Plot Margin
    plot.margin = c(10, 25, 10, 10) #c(top, right, bottom, left)
  )
)
</code></pre>
</div>


</div> <!-- END .code-group-detail -->

<script>
  const selectDetail = document.getElementById("plotFilterDetail");
  const boxesDetail = document.querySelectorAll(".code-group-detail .code-box");

  function showDetail() {
    boxesDetail.forEach(box => box.style.display = "none");
    const selected = selectDetail.value;
    const box = document.getElementById(selected);
    if (box) box.style.display = "block";
  }

  selectDetail.addEventListener("change", showDetail);
  showDetail();
</script>
<!-- END -->
```
</details>

<br>

# Stack Plot
<details>
  <summary class="toggle-summary">💻 Stack Plot Codes</summary>
```{=html}
<!-- START: Stack Plot Filter UI -->
<style>
  label { font-weight: bold; }
  select { font-size: 16px; margin-bottom: 20px; padding: 5px 10px; width: 300px;}
  pre { background-color: #f4f4f4; padding: 15px; border-left: 5px solid #1C3E5D; overflow-x: auto; }
  .code-box { display: none; }
</style>

<label for="plotFilterStack">Choose Codes:</label>
<select id="plotFilterStack">
  <option value="default_stack">Default</option>
  <option value="unstack_plot">Unstack Plot</option>
  <option value="advanced_stackplot">Advanced Stack Plot</option>
</select>

<div class="stack-code-blocks">

<div id="default_stack" class="code-box">
  <p>This R script is designed to create a stack plot suitable for decomposition analysis—such as welfare decomposition from header <code>A</code> of <code>-WEL.har</code>.</p>
  
  <pre><code>
# For help function use: ?stack_plot
stack.data <- har.plot.data[["A"]]  # Replace with your actual dataframe

stack_plot(
  data                      = stack.data,
  x_axis_from               = "Region",        # Column used for the x-axis
  filter_var                = NULL,            # Optional column to filter data based on x-axis
  stack_value_from          = "COLUMN",        # Column that defines the components of the stack plot
  show_total                = TRUE,            # Show the total value label in the stack plot
  unstack_plot              = FALSE,           # If TRUE, unstack the bars and display them separately (comparison style)
  split_by                  = FALSE,           # Column(s) used to split data into separate plots. FALSE disables splitting
  panel_var                 = "Experiment",    # Column used for paneling (faceting)
  top_impact                = NULL,            # Optionally limit to top-N most impactful entries per panel
  invert_axis              = FALSE,           # Whether to invert the panel (facet) order
  separate_figure           = FALSE,           # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,            # Use the description as the variable name (e.g., qgdp becomes Real GDP)
  add_var_info              = FALSE,           # Add variable code in parentheses (e.g., Real GDP (qgdp))
  export_picture            = FALSE,           # Export the plots as image files
  export_as_pdf             = FALSE,           # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,
  
  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly     
  export_config = create_export_config(
    width  = 28,             # Width of the output plot in inches
    height = 15              # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "full",         # option: standard (default), prefix, suffix, full, dynamic
      text = "Welfare Decomposition",
      sep  = ""
    ),
    color_tone    = "purdue",   # Color palette for the plot
    all_font_size = 1,          # Scale for all font sizes in the plot 
    panel_rows    = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols    = NULL        # Number of columns for the panel layout, NULL for automatic calculation  
  )
)
</code></pre>
  </div>
  
  <div id="unstack_plot" class="code-box">
  <p>This R script is designed to create an unstacked plot, suitable for further analyzing decomposition results at a disaggregated level (e.g., by country).</p>
  
  <pre><code>
  # For help function use: ?stack_plot
  stack.data <- har.plot.data[["A"]]  # Replace with your actual dataframe

stack_plot(
  data                      = stack.data,
  x_axis_from               = "Region",        # Column used for the x-axis
  filter_var                = NULL,            # Optional column to filter data based on x-axis
  stack_value_from          = "COLUMN",        # Column that defines the components of the stack plot
  show_total                = TRUE,            # Show the total value label in the stack plot
  unstack_plot              = TRUE,            # If TRUE, unstack the bars and display them separately (comparison style)
  split_by                  = "Region",        # Column(s) used to split data into separate plots (e.g., one plot per region)
  panel_var                 = "Experiment",    # Column used for paneling (faceting)
  top_impact                = NULL,            # Optionally limit to top-N most impactful entries per panel
  invert_axis              = FALSE,           # Whether to invert the panel (facet) order
  separate_figure           = FALSE,           # Whether to generate a separate figure for each panel
  var_name_by_description   = TRUE,            # Use the description as the variable name
  add_var_info              = FALSE,           # Add variable code in parentheses
  export_picture            = FALSE,           # Export the plots as image files
  export_as_pdf             = FALSE,           # Export the plots as PDF. Use "merged" to combine all plots into one PDF
  output_path               = output.folder,
  
  # Output Configurations
  ## Try adjusting widgth and height if output is too dense, too small, or not displayed properly     
  export_config = create_export_config(
    width  = 28,             # Width of the output plot in inches
    height = 15              # Height of the output plot in inches
  ),
  
  plot_style_config = create_plot_style(
    title_format = create_title_format(
      type = "full",         # option: standard (default), prefix, suffix, full, dynamic
      text = "Welfare Decomposition",
      sep  = ""
    ),
    color_tone    = "purdue",   # Color palette for the plot
    all_font_size = 1,          # Scale for all font sizes in the plot 
    panel_rows    = 1,          # Number of rows for the panel layout, NULL for automatic calculation  
    panel_cols    = NULL        # Number of columns for the panel layout, NULL for automatic calculation  
  )
)
</code></pre>
  </div>
    


<div id="advanced_stackplot" class="code-box">
<p>This R script is designed for full customization—everything must be defined from scratch. Please refer to the <strong>Plot Style Configs</strong> section before using it.</p>

<pre><code>
# For help function use: ?stack_plot
stack_plot_data <- har.plot.data[["A"]]  # Replace with your actual dataframe name

adv.stack.plot <- stack_plot(
  data = detail.data,
  x_axis_from             = "Colname",
  filter_var              = NULL,
  split_by                = NULL,
  stack_value_from        = "Colname",
  unstack_plot            = TRUE,
  panel_var               = "Experiment",
  variable_col            = "Variable",
  unit_col                = "Unit",
  desc_col                = "Description",
  top_impact              = NULL,
  invert_axis            = FALSE,
  separate_figure         = FALSE,
  var_name_by_description = FALSE,
  add_var_info            = FALSE,
  export_picture          = FALSE,
  export_as_pdf           = FALSE,
  output_path             = "/your/path",

  # Output Configurations
  export_config           = create_export_config(
    width = NULL,
    height = NULL,
    dpi = 300,
    bg = "white",
    limitsize = FALSE
  )
  
  # All Plot Configurations
  plot_style_config = create_plot_style(
    
    # Title settings
    show_title = TRUE,
    title_face = "bold",
    title_size = 20,
    title_hjust = 0.5,
    add_unit_to_title = TRUE,
    title_margin = c(10, 0, 10, 0), #c(top, right, bottom, left)
    
    title_format = create_title_format(
      type = "standard", #option: standard (default), prefix, suffix, full, dynamic
      text = "",
      sep = ""
    ),
    
    # X-Axis settings
    show_x_axis_title = TRUE,
    x_axis_title_face = "bold",
    x_axis_title_size = 16,
    x_axis_title_margin = c(25, 25, 0, 0), #c(top, right, bottom, left)
    show_x_axis_labels = TRUE,
    x_axis_text_face = "plain",
    x_axis_text_size = 14,
    x_axis_text_angle = 0,
    x_axis_text_hjust = 0,
    x_axis_description = "",
    
    # Y-Axis settings
    show_y_axis_title = TRUE,
    y_axis_title_face = "bold",
    y_axis_title_size = 16,
    y_axis_title_margin = c(25, 25, 0, 0), #c(top, right, bottom, left)
    show_y_axis_labels = TRUE,
    y_axis_text_face = "plain",
    y_axis_text_size = 14,
    y_axis_text_angle = 0,
    y_axis_text_hjust = 0,
    y_axis_description = "",
    show_axis_titles_on_all_facets = TRUE,
    
    # Value Labels
    show_value_labels = TRUE,
    value_label_face = "plain",
    value_label_size = 5,
    value_label_position = "above",
    value_label_decimal_places = 2,
    
    # Legend
    show_legend = FALSE,
    show_legend_title = FALSE,
    legend_position = "bottom",
    legend_title_face = "bold",
    legend_text_face = "plain",
    legend_text_size = 14,
    
    # Panel Strip
    strip_face = "bold",
    strip_text_size = 16,
    strip_background = "lightgrey",
    strip_text_margin = c(10, 0, 10, 0), #c(top, right, bottom, left)
    
    # Panel Layout
    panel_spacing = 2,
    panel_rows = NULL,
    panel_cols = NULL,
    theme = NULL,
    
    # Colors and Grid 
    color_tone = NULL,
    color_palette_type = "qualitative", #option: qualitative, sequential, diverging
    positive_color = "#2E8B57",
    negative_color = "#CD5C5C",
    background_color = "white",
    grid_color = "grey90",
    show_grid_major_x = FALSE,
    show_grid_major_y = FALSE,
    show_grid_minor_x = FALSE,
    show_grid_minor_y = FALSE,
    
    # Zero Line
    show_zero_line = TRUE,
    zero_line_type = "dashed",
    zero_line_color = "black",
    zero_line_size = 0.5,
    zero_line_position = 0,
    
    # Bar Chart
    bar_width = 0.9,
    bar_spacing = 0.9,
    
    # Scale Settings
    scale_limit = NULL,
    scale_increment = NULL,
    
    # Scale Expansion
    expansion_y_mult = c(0.05, 0.1),
    expansion_x_mult = c(0.05, 0.05),
    
    # Font Size Control
    all_font_size = 1,
    
    # Data Sorting
    sort_data_by_value = FALSE,
    
    # Plot Margin
    plot.margin = c(10, 25, 10, 10) #c(top, right, bottom, left)
  )
)
</code></pre>
</div>

</div> <!-- END .stack-code-blocks wrapper -->

<script>
  const select = document.getElementById("plotFilterStack");
  const wrapper = document.querySelector(".stack-code-blocks");
  const boxes = wrapper.querySelectorAll(".code-box");

  function showSelectedBox() {
    boxes.forEach(box => box.style.display = "none");
    const selected = select.value;
    const target = document.getElementById(selected);
    if (target) target.style.display = "block";
  }

  select.addEventListener("change", showSelectedBox);
  showSelectedBox();
</script>
```
</details>


# (Optional) Plot Style Configs {.unnumbered}

## Step-by-step {.unnumbered}

- Run the following chunks to view all available configurations.
```{r, eval=FALSE}
get_all_config()
```

- Rename the list outputs `my_export_config` and `my_style_config` to any names you prefer; you can create as many styles as needed.

- Enter the name of your custom style list into the plot function, while other settings in `(...)` remain unchanged, as shown in the sample below:

```{r, eval=FALSE}
comparison_plot <- (...,
                    export_config = my_export_config,
                    plot_style_config = my_style_config
                    )
```


```{=html}
<script>
// SCRIPT 1: Copy Code Button
window.addEventListener("load", function () {
  document.querySelectorAll("pre code").forEach(function (codeBlock) {
    const button = document.createElement("button");
    button.className = "copy-code-button";
    button.type = "button";
    button.innerText = "Copy";
    button.style.position = "absolute";
    button.style.top = "4px";
    button.style.right = "4px";
    button.addEventListener("click", () => {
      navigator.clipboard.writeText(codeBlock.innerText).then(() => {
        button.innerText = "Copied!";
        setTimeout(() => (button.innerText = "Copy"), 1500);
      });
    });
    const pre = codeBlock.parentNode;
    pre.style.position = "relative";
    pre.insertBefore(button, codeBlock);
  });
});

// SCRIPT 2: Hide Navbar on Scroll Down
document.addEventListener("DOMContentLoaded", function () {
  let prevScrollPos = window.pageYOffset;
  const navbar = document.querySelector(".navbar");
  
  if (navbar) {
    // Set initial styles for smooth transition
    navbar.style.transition = "top 0.3s";
    navbar.style.position = "fixed";
    navbar.style.width = "100%";
    navbar.style.zIndex = "1000";
    
    window.addEventListener("scroll", function () {
      const currentScrollPos = window.pageYOffset;
      if (prevScrollPos > currentScrollPos) {
        // Scrolling up
        navbar.style.top = "0";
      } else {
        // Scrolling down
        navbar.style.top = "-70px";
      }
      prevScrollPos = currentScrollPos;
    });
  }
});

// SCRIPT 3: Center Navbar Items
document.addEventListener('DOMContentLoaded', function() {
  // Create a container to center the navbar items
  var navbar = document.querySelector('.navbar-collapse');
  var navLinks = document.querySelectorAll('.navbar-left li');
  var navRight = document.querySelector('.navbar-right');
  
  // Apply styles to center the main navigation
  if (navbar && navLinks.length > 0) {
    var mainNav = document.querySelector('.navbar-left');
    
    // Add a wrapper div to center the main nav
    var centerWrapper = document.createElement('div');
    centerWrapper.className = 'nav-center-wrapper';
    centerWrapper.style.display = 'flex';
    centerWrapper.style.justifyContent = 'center';
    centerWrapper.style.flex = '1';
    
    // Move the main navbar inside this wrapper
    if (mainNav && mainNav.parentNode) {
      mainNav.parentNode.insertBefore(centerWrapper, mainNav);
      centerWrapper.appendChild(mainNav);
    }
  }
});
</script>
```
